Charity analysis

### 2022-07-19 Shiny/Test/Flexdashboard rows.Rmd
Icon fix.

```{r setup, include=FALSE}
# Packages using pacman
if (!require("pacman")) install.packages("pacman"); library(pacman)
p_load(shiny, tidyverse, scales, rvest, janitor, plotly, readxl,
       flexdashboard, MetBrewer, fontawesome, htmltools)
# Using package fontawesome for fontawesome icons
htmltools::tagList(fontawesome::fa_html_dependency())
```

@@

    # Creating KPI_admin value
    KPI_admin <- reactive({exceldata() |> 
           mutate(
      KPI_admin =
        str_c(
         format(
          (expenses_administrative / expenses_program_services *100), digits = 3
          ), "%"
         )
      ) |> 
      filter(year == max(year)) |> 
       select(KPI_admin) |> 
        str_flatten()
         })

@@

    # Duplicate value boxes for testing
    output$KPI_box2 <- renderValueBox({
      valueBox(
        value = KPI_admin(),
        caption = "danger",
        color = "danger",
        icon = "fa-random"
      )
    })
    output$KPI_box3 <- renderValueBox({
      valueBox(
        value = KPI_admin(),
        caption = "success",
        color = "success",
        icon = "fa-random"
      )
    })

    output$KPI_box4 <- renderValueBox({
      valueBox(
        value = KPI_admin(),
        caption = "info",
        color = "info",
        icon = "fa-random"
      )})

>>>>

```{r setup, include=FALSE}
# Loading packages using pacman to ensure they're all installed
if (!require("pacman")) install.packages("pacman"); library(pacman)
p_load(shiny, tidyverse, scales, rvest, janitor, plotly, readxl,
       flexdashboard, MetBrewer, fontawesome, htmltools)
# Using fontawesome for more up-to-date fontawesome icons
htmltools::tagList(fontawesome::fa_html_dependency())
```

@@

    # Creating KPI_admin value
    KPI_admin <- reactive({exceldata() |> 
           mutate(
      KPI_admin =
        str_c( # Using str_c() to concatenate value and % sign
         format( # shortening(lengthening) the resulting value
           # calculating the value
          (expenses_administrative / expenses_program_services *100), digits = 3
          ), "%"
         )
      ) |> 
      filter(year == max(year)) |> # selecting latest available year
       select(KPI_admin) |> # dropping all other variables
        str_flatten() # turning into a single string
         })

@@

    # Duplicate value boxes for testing
    output$KPI_box2 <- renderValueBox({
      valueBox(
        value = KPI_admin(),
        caption = "danger",
        color = "danger",
        icon = "fas fa-dog"
      )

    })
    output$KPI_box3 <- renderValueBox({
      valueBox(
        value = KPI_admin(),
        caption = "success",
        color = "success",
        icon = "fas fa-coffee"
      )
    })

    output$KPI_box4 <- renderValueBox({
      valueBox(
        value = KPI_admin(),
        caption = "info",
        color = "info",
        icon = "fas fa-skull-crossbones"
      )})
